### 2016-03-19 section/5_exper.tex
check in template changing and some content in experiments

First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
The extraction is conducted by XXX.
We did not use the remaining 27 bugs listed in Table \ref{tab:root}
as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract XXX. 
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}.

Second, we evaluate \Tool on 21 out of the xx bugs in the benchmark
suite of Toddler \cite{Alabama}.
All of these bugs come from Java programs. We extract XXX (how did you
extract exactly?) and re-implement in C++. Each extracted benchmark 
contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a larget set of
repeatable inefficient loop problems.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
XXX (what can we say about Toddler benchmark set here?)

@@

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287 and Apache\#53622, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
only changed the data structure, which eliminated both types of inefficiency,
in case of MySQL\#27287, or the main type of inefficiency, in case of Apache\#53622.

>>>>

First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
We extract the original data structures and caller-callees, 
and translate them into C++ programs, following the original data flow and control flow dependence. 
We design unit test inputs based on inputs in bug reports and our understanding to run our re-implemented codes.  
We did not use the remaining 27 bugs listed in Table \ref{tab:root}
as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract. 
For example, some bugs can only be triggered on Windows, and some bugs depend on .Net libraries. 
For example, we have bugs related to GUI widgets, and it is too complex to re-implement these GUI widgets. 
We also have bugs, in which buggy loops traverse graphs. 
Without repeating these bugs, it is too difficult to figure out graph structures just through code reading.  
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}.

Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama}.
We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
We re-implement these basic data structures following the recent version of openjdk. 
We re-implement the buggy codes and test inputs in the bug reports, 
following the original data flow and control flow dependence. 
For two benchmarks, there are only 4 loops in our re-implemented versions. For all other benchmarks, there are no less than 5 loops. 
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a large set of
repeatable inefficient loop problems.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)
For all benchmarks from Toddler project, 
statistical debugging ranks the real root-cause loop as Top 1 or Top 2 (for cases where there are two root-cause loops). 
During our accuracy experiments, we will apply LDoctor to top 5 loops identified by statistical debugging. 
For some re-implemented bugs, there may be less than 5 loops returned by statistical debugging. 
The number of loops we analyze for the first benchmark set is 64, and the number of loops we analyze for Toddler benchmark set is 103.

@@

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
only changed the data structure, which eliminated both types of inefficiency,
in case of MySQL\#27287. 
For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? Inefficient. 
\Tool suggests batching and changing data structure respectively. 
In practice, developers only fix the main root cause loop, by using changing data structure.
